### 2019-05-24 5_evaluation.tex
Fiddle with figure placement.
Switch to new GPU figure.

@@

Figure~\ref{fig:cuda-efficiency} shows a comparison between the MPI
and MPI+CUDA implementations on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which compares favorably with the officially reported number
$4.761 \times 10^{12}$. The CPU kernel achieves $5.726 \times 10^{11}$
FLOP/s. Note that the x-axis is measured in the number of FLOPs
performed during the run, as the GPU kernels must be given more work to
achieve peak performance.

>>>>

Figure~\ref{fig:cuda-efficiency} shows a comparison between the MPI
and MPI+CUDA implementations on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which compares favorably with the officially reported number
$4.761 \times 10^{12}$. The CPU kernel achieves $5.726 \times 10^{11}$
FLOP/s. Note that the CPU and GPU kernels perform different numbers of
operations as the GPU must be given more work to achieve peak
performance. The x-axis in Figure~\ref{fig:cuda-efficiency} has been
normalized so that the number of FLOPs is constant for a given problem
size.

@@
